COVID-19 and Online Learning Tools

### 2021-12-28 Paper_online_Learning.tex
working on results

The visual representation of Google Trend search quiries of COVID-19 related terms worldwide shows that the highest peak coincided with the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (b)). Surprisingly, the search volume index graph for distanced education related terms also shows a similar spike at the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). This highlights the impact of COVID-19 pandemic on distance education.

According to \textcite{moore2011learning}, ``distance education'' is the most renowned descriptor used when referencing distance learning. However, both \textcite{benson2002usability} and \textcite{conrad2002deep} introduced ``online learning'' as the most ``recent version'', ``newer version'' and ``improved version'' of distance learning. The Google Trend search patterns corresponds to the term ``online learning'' confirm the above claim as it is the most searched distance education related term throughout the COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). Despite quantitative differences in terms of relative search volume, the series generated by the two terms ``Distance learning'' and ``online teaching'' demonstrate a similar trend during the study period. COVID-19 related web searches declined in the months after the WHO announcement of the COVID-19 pandemic, despite the increase in COVID-19 cases. A similar decline can be observed in distance education related terms (Figures \ref{fig:distanceLearningWorldAnalysis}). This confirms the life cycle of Google Trend search patterns introduced in \textcite{jarynowski2020perception}. Further, a second peak was observed only in education related terms after the WHO announcement of the COVID-19 pandemic. This could be due to the near total closures of schools happened with the declaration of COVID-19 as a pandemic.

@@

A pairwise comparison was performed using Dynamic Time Warping algorithm. Under this approach, two time series are stretched or compressed locally in order to make one resemble the other as much as possible. The distance between the two series is then computed by summing the distances of individual aligned elements \autocite{giorgino2009computing}. Two pairwise comparisons, ``corona'' with ``online learning'' and ``covid'' with ``online learning'' were conducted to see the impact of COVID-19 on distance education. Both pairwise comparisons show a significant areas of overlap and a similar dynamic pattern (Figures \ref{fig:dtw1} (a) and \ref{fig:dtw2} (a)). The normalized distance between the two series in the two comparisons are 0.1326197 and 0.1828299, respectively. This also provides further confirmation for the similarity of the Google Trend search profiles. this highlight the sudden public attention towards both aspects, COVID-19 and distance education, eventhough distance education has a long history in contrast to COVID-19.

The entirety of the blue warping path flows through green pastures further confirms the similarity between the search patterns related to COVID-19 and distance education (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)). The orange volcanic topography that highlights regions of nonalignment of series in question if mapped through this region demonstrate a significant difference in online search behaviours before and after the COVID-19 pandemic (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)).

The degree of digression of blue line from the ideal 45-degree straight line indicates a dissimilarity of the two time
series (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)). In late 2019 the infection was recognized as a virus which is genetically related to the corona virus responsible for the Severe Acute Respiratory Syndrome (SARS) outbreak of 2003 which infected over 8,000 people from different countries that resulted more than 700 deaths worldwide \autocite{ciotti2019covid}.When the virus was know as ``corona'' it was not a global concern and was mostly limited to China. During that time people did not pay much attention to online learning as conventional classroom learning approach was the most popular teaching learning strategy prior to COVID-19 pandemic. This is evident from the rough flat line from approximately 120 to 170 on the Query Index axis in Figure \ref{fig:dtw1} (b).

Later, with the spread of the virus worldwide, WHO named it as COVID-19 (COrona VIrus Diagnosed in 2019) and then declared it as a pandemic on March 11, 2020. With that, a near total closure of schools were observed all around the world (Figures \ref{fig:covidImpactWorld}). With this sudden unexpected massive shutdown, online learning also became an equally important global concern, similar to COVID-19 pandemic. This similar behaviour in public attention towards both aspects is confirmed by the blue line that falls on near 45-degree line from approximately 120 to 150 on the Query Index axis in Figure \ref{fig:dtw2} (b). This also confirms the impact of COVID-19 on distance education and online learning.

Next, a cross correlation analysis was performed to estimate the lag time between COVID-19 related terms and the distance education related terms (Figures \ref{fig:ccfAnalysis}). A close relationship was evident between COVID-19 related search patterns and the search patterns of the terms ``Online learning'', ``Distance learning'' and ``Online teaching''. The significant cross-correlation coefficients at lag zero confirms contemporaneous relationship between the COVID-19 related search terms and distance learning related search terms. The significant cross correlation values at lag one or two also confirms the sudden impact of COVID-19 pandemic on distance education related public concerns (Figures \ref{fig:ccfAnalysis} (a) - (c) and (f) - (h)). However, no significant synchronization was observed between the COVID-19 related search trends and the search patterns of ``distance education'' or ``online proctoring'' (Figures \ref{fig:ccfAnalysis} (d), (i), (e), (j)).

>>>>

The visual representation of Google Trend search queries of COVID-19 related terms worldwide shows that the highest peak coincided with the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (b)). Surprisingly, the search volume index graph for distance education related terms also shows a similar spike at the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). This highlights the impact of the COVID-19 pandemic on distance education.

According to \textcite{moore2011learning}, ``distance education'' is the most renowned term used when referencing distance learning. However, both \textcite{benson2002usability} and \textcite{conrad2002deep} introduced ``online learning'' as the most ``recent version,'' ``newer version'' and ``improved version'' of distance learning. The Google Trend search patterns correspond to the term ``online learning'' confirm the above claim as it is the most searched distance education related term throughout the COVID-19 pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). Despite quantitative differences in terms of relative search volume, the series generated by the two terms ``distance learning'' and ``online teaching'' demonstrate a similar trend during the study period. COVID-19 related web searches declined in the months after the WHO announcement of the COVID-19 pandemic, despite the increase in COVID-19 cases. A similar decline can be observed in distance education-related terms (Figures \ref{fig:distanceLearningWorldAnalysis}). This confirms the life cycle of Google Trend search patterns introduced in \textcite{jarynowski2020perception}. Further, a second peak was observed only in education related terms after the WHO announcement of the COVID-19 pandemic. This could be due to the nearly total closures of schools that happened with the declaration of COVID-19 as a pandemic.

@@

A pairwise comparison was performed using the Dynamic Time Warping algorithm. Under this approach, two time series are stretched or compressed locally in order to make one resemble the other as much as possible. The distance between the two series is then computed by summing the distances of individual aligned elements \autocite{giorgino2009computing}. Two pairwise comparisons, ``corona'' with ``online learning'' and ``covid'' with ``online learning'' were conducted to see the impact of COVID-19 on distance education. Both pairwise comparisons show significant areas of overlap and a similar dynamic pattern (Figures \ref{fig:dtw1} (a) and \ref{fig:dtw2} (a)). The normalized distance between the two series in the two comparisons is 0.1326197 and 0.1828299, respectively. This also provides further confirmation of the similarity of the Google Trend search profiles. This highlights the sudden public attention towards both aspects, COVID-19 and distance education, even though distance education has a long history in contrast to COVID-19.

The entirety of the blue warping path flows through green pastures, further confirming the similarity between the search patterns related to COVID-19 and distance education (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)). The orange volcanic topography that highlights regions of nonalignment of the series in question if mapped through this region demonstrates a significant difference in online search behaviour before and after the COVID-19 pandemic (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)).

The degree of digression of the blue line from the ideal 45-degree straight line indicates a dissimilarity between the two time
series (Figures \ref{fig:dtw1} (b) and \ref{fig:dtw2} (b)). In late 2019 the infection was recognized as a virus which is genetically related to the coronavirus responsible for the Severe Acute Respiratory Syndrome (SARS) outbreak of 2003, which infected over 8,000 people from different countries and resulted in more than 700 deaths worldwide \autocite{ciotti2019covid}.When the virus was known as ``corona'', it was not a global concern and was mostly limited to China. During that time, people did not pay much attention to online learning as conventional classroom learning approach was the most popular teaching learning strategy prior to the COVID-19 pandemic. This is evident from the rough flat line from approximately 120 to 170 on the Query Index axis in Figure \ref{fig:dtw1} (b).

Later, with the spread of the virus worldwide, WHO named it COVID-19 (COrona VIrus Diagnosed in 2019) and then declared it a pandemic on March 11, 2020. With that, a near total closure of schools was observed all around the world (Figures \ref{fig:covidImpactWorld}). With this sudden and unexpected massive shutdown, online learning also became an equally important global concern, similar to the COVID-19 pandemic. This similar behaviour in public attention towards both aspects is confirmed by the blue line that falls on a near 45-degree line from approximately 120 to 150 on the Query Index axis in Figure \ref{fig:dtw2} (b). This also confirms the impact of COVID-19 on distance education and online learning.

Next, a cross correlation analysis was performed to estimate the lag time between COVID-19 related terms and the distance education related terms (Figures \ref{fig:ccfAnalysis}). A close relationship was evident between COVID-19 related search patterns and the search patterns for the terms ``Online learning'', ``Distance learning'' and ``Online teaching''. The significant cross-correlation coefficients at lag zero confirm the contemporaneous relationship between the COVID-19 related search terms and distance learning related search terms. The significant cross correlation values at lag one or two also confirm the sudden impact of the COVID-19 pandemic on distance education related public concerns (Figures \ref{fig:ccfAnalysis} (a) - (c) and (f) - (h)). However, no significant synchronization was observed between the COVID-19 related search trends and the search patterns of ``distance education'' or ``online proctoring'' (Figures \ref{fig:ccfAnalysis} (d), (i), (e), (j)).

### 2021-12-28 main.Rmd
working on results

The visual representation of Google Trend search quiries of COVID-19 related terms worldwide shows that the highest peak coincided with the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (b)). Surprisingly, the search volume index graph for distanced education related terms also shows a similar spike at the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). This highlights the impact of COVID-19 pandemic on distance education.

According to @moore2011learning, "distance education" is the most renowned descriptor used when referencing distance learning. However, both  @benson2002usability and @conrad2002deep introduced "online learning"  as the most "recent version", "newer version" and "improved version" of distance learning. The Google Trend search patterns corresponds to the term "online learning" confirm the above claim as it is the most searched distance education related term throughout the COVID-19 pandemic  (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). Despite quantitative differences in terms of relative search volume, the series generated by the two terms "Distance learning" and "online teaching" demonstrate a similar trend during the study period. COVID-19 related web searches declined in the months after the WHO announcement of the COVID-19 pandemic, despite the increase in COVID-19 cases. A similar decline can be observed in distance education related terms  (Figures \ref{fig:distanceLearningWorldAnalysis}). This confirms the life cycle of Google Trend search patterns introduced in @jarynowski2020perception. Further,  a second peak was observed only in education related terms  after the WHO announcement of the COVID-19 pandemic. This could be due to the near total closures of schools happened  with the declaration of  COVID-19 as a pandemic.

@@

A pairwise comparison was performed  using  Dynamic Time Warping algorithm. Under this approach, two time series are stretched or compressed  locally in order to make one resemble the other as much as possible. The distance between the two series is then computed by summing the distances of individual aligned elements [@giorgino2009computing].  Two pairwise comparisons, "corona"  with "online learning" and   "covid" with "online learning" were conducted to see the impact  of COVID-19 on distance education. Both pairwise comparisons show a significant  areas of overlap and a similar dynamic pattern (Figures \ref{fig:dtw1} (a) and  \ref{fig:dtw2} (a)). The normalized distance between the two series in the two comparisons are  0.1326197 and 0.1828299, respectively. This also provides further confirmation for  the similarity of the Google Trend  search profiles. this highlight the sudden public attention towards both aspects, COVID-19 and distance education, eventhough distance education has a long history in contrast to COVID-19.

The entirety of the blue warping path flows through green pastures further confirms the similarity between the search patterns related to COVID-19 and distance education (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)). The orange volcanic topography that highlights regions of nonalignment of series in question if mapped through this region demonstrate a significant difference in online search behaviours before and after the COVID-19 pandemic (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)).

The degree of digression of blue line from the ideal 45-degree straight line indicates a dissimilarity of the two time
series (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)). In late 2019 the infection was recognized as a virus which is genetically related to the corona virus responsible for the Severe Acute Respiratory Syndrome (SARS) outbreak of 2003 which infected over 8,000 people from different countries that resulted more than 700 deaths worldwide [@ciotti2019covid].When the virus was know as "corona" it was not a global concern and was mostly limited to China. During that time people did not pay much attention to online learning as  conventional classroom learning approach was the most popular teaching learning strategy prior to COVID-19 pandemic. This is evident from  the rough flat line from approximately 120 to 170 on the Query Index axis in Figure \ref{fig:dtw1} (b).

Later, with the spread of the virus worldwide, WHO  named it as  COVID-19 (COrona VIrus Diagnosed in 2019) and then declared it as a pandemic on March 11, 2020. With that, a near total closure of schools were observed all around the world (Figures \ref{fig:covidImpactWorld}).  With this sudden unexpected massive shutdown, online learning  also became an equally important global concern, similar to COVID-19 pandemic.  This similar  behaviour in  public attention towards both aspects is confirmed by the blue line that falls on near 45-degree line  from approximately 120 to 150 on the Query Index axis in Figure \ref{fig:dtw2} (b). This also confirms the impact of COVID-19 on distance education and online learning.

Next, a cross correlation analysis was performed to estimate the lag time between COVID-19 related terms and the distance education related terms (Figures \ref{fig:ccfAnalysis}). A close relationship was evident between COVID-19 related search patterns and the search patterns of the terms "Online learning", "Distance learning" and "Online teaching". The significant cross-correlation coefficients  at lag zero confirms  contemporaneous relationship between the COVID-19 related search terms and distance learning related search terms. The significant cross correlation values at lag one or two also confirms the sudden impact of COVID-19 pandemic on distance education related public concerns (Figures \ref{fig:ccfAnalysis} (a) - (c) and (f) - (h)).  However, no significant  synchronization was observed  between the COVID-19 related search trends and the search patterns of "distance education" or "online proctoring" (Figures \ref{fig:ccfAnalysis} (d), (i), (e), (j)).

>>>>

The visual representation of Google Trend search queries of COVID-19 related terms worldwide shows that the highest peak coincided with the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (b)). Surprisingly, the search volume index graph for distance education related terms also shows a similar spike at the start of the pandemic (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). This highlights the impact of the COVID-19 pandemic on distance education.

According to @moore2011learning, "distance education" is the most renowned term used when referencing distance learning. However, both  @benson2002usability and @conrad2002deep introduced "online learning"  as the most "recent version," "newer version" and "improved version" of distance learning. The Google Trend search patterns correspond to the term "online learning" confirm the above claim as it is the most searched distance education related term throughout the COVID-19 pandemic  (Figures \ref{fig:distanceLearningWorldAnalysis} (c)). Despite quantitative differences in terms of relative search volume, the series generated by the two terms "distance learning" and "online teaching" demonstrate a similar trend during the study period. COVID-19 related web searches declined in the months after the WHO announcement of the COVID-19 pandemic, despite the increase in COVID-19 cases. A similar decline can be observed in distance education-related terms  (Figures \ref{fig:distanceLearningWorldAnalysis}). This confirms the life cycle of Google Trend search patterns introduced in @jarynowski2020perception. Further,  a second peak was observed only in education related terms  after the WHO announcement of the COVID-19 pandemic. This could be due to the nearly total closures of schools that happened  with the declaration of  COVID-19 as a pandemic.

@@

A pairwise comparison was performed  using the Dynamic Time Warping algorithm. Under this approach, two time series are stretched or compressed  locally in order to make one resemble the other as much as possible. The distance between the two series is then computed by summing the distances of individual aligned elements [@giorgino2009computing].  Two pairwise comparisons, "corona"  with "online learning" and   "covid" with "online learning" were conducted to see the impact  of COVID-19 on distance education. Both pairwise comparisons show significant  areas of overlap and a similar dynamic pattern (Figures \ref{fig:dtw1} (a) and  \ref{fig:dtw2} (a)). The normalized distance between the two series in the two comparisons is  0.1326197 and 0.1828299, respectively. This also provides further confirmation of  the similarity of the Google Trend  search profiles. This highlights the sudden public attention towards both aspects, COVID-19 and distance education, even though distance education has a long history in contrast to COVID-19.

The entirety of the blue warping path flows through green pastures, further confirming the similarity between the search patterns related to COVID-19 and distance education (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)). The orange volcanic topography that highlights regions of nonalignment of the series in question if mapped through this region demonstrates a significant difference in online search behaviour before and after the COVID-19 pandemic (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)).

The degree of digression of the blue line from the ideal 45-degree straight line indicates a dissimilarity between the two time
series (Figures \ref{fig:dtw1} (b) and  \ref{fig:dtw2} (b)). In late 2019 the infection was recognized as a virus which is genetically related to the coronavirus responsible for the Severe Acute Respiratory Syndrome (SARS) outbreak of 2003, which infected over 8,000 people from different countries and resulted in more than 700 deaths worldwide [@ciotti2019covid].When the virus was known as "corona", it was not a global concern and was mostly limited to China. During that time, people did not pay much attention to online learning as  conventional classroom learning approach was the most popular teaching learning strategy prior to the COVID-19 pandemic. This is evident from  the rough flat line from approximately 120 to 170 on the Query Index axis in Figure \ref{fig:dtw1} (b).

Later, with the spread of the virus worldwide, WHO  named it COVID-19 (COrona VIrus Diagnosed in 2019) and then declared it a pandemic on March 11, 2020. With that, a near total closure of schools was observed all around the world (Figures \ref{fig:covidImpactWorld}).  With this sudden and unexpected massive shutdown, online learning  also became an equally important global concern, similar to the COVID-19 pandemic.  This similar  behaviour in  public attention towards both aspects is confirmed by the blue line that falls on a near 45-degree line  from approximately 120 to 150 on the Query Index axis in Figure \ref{fig:dtw2} (b). This also confirms the impact of COVID-19 on distance education and online learning.

Next, a cross correlation analysis was performed to estimate the lag time between COVID-19 related terms and the distance education related terms (Figures \ref{fig:ccfAnalysis}). A close relationship was evident between COVID-19 related search patterns and the search patterns for the terms "Online learning", "Distance learning" and "Online teaching". The significant cross-correlation coefficients  at lag zero confirm the contemporaneous relationship between the COVID-19 related search terms and distance learning related search terms. The significant cross correlation values at lag one or two also confirm the sudden impact of the COVID-19 pandemic on distance education related public concerns (Figures \ref{fig:ccfAnalysis} (a) - (c) and (f) - (h)).  However, no significant  synchronization was observed  between the COVID-19 related search trends and the search patterns of "distance education" or "online proctoring" (Figures \ref{fig:ccfAnalysis} (d), (i), (e), (j)).
